### 2019-05-29 README.Rmd
Change status from WIP to Active

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2630836.svg){data-external="1"}](https://doi.org/10.5281/zenodo.2630836)
[![CircleCI](https://circleci.com/gh/ropensci/citesdb/tree/master.svg?style=shield){data-external="1"}](https://circleci.com/gh/ropensci/citesdb)
[![](https://badges.ropensci.org/292_status.svg)](https://github.com/ropensci/software-review/issues/292)
[![codecov](https://codecov.io/gh/ropensci/citesdb/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/ropensci/citesdb)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)

>>>>

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2630836.svg){data-external="1"}](https://doi.org/10.5281/zenodo.2630836)
[![CircleCI](https://circleci.com/gh/ropensci/citesdb/tree/master.svg?style=shield){data-external="1"}](https://circleci.com/gh/ropensci/citesdb)
[![](https://badges.ropensci.org/292_status.svg)](https://github.com/ropensci/software-review/issues/292)
[![codecov](https://codecov.io/gh/ropensci/citesdb/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/ropensci/citesdb)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
